Dominance Regions for Rank Two Cluster Algebras

### 2022-06-06 dominance_regions.tex
I'm dumb, we adjusted our initial cluster exactly for this reason (changed it back in Lemma 4.1)
Done up to section 5

  Here we explicitly compute the dominance regions $\cP_\lambda$.
  When $\lambda$ is not imaginary, the dominance region is particularly simple.
  \begin{lemma}
    \label{le:cluster monomials}
    If $\lambda\in\ZZ^2\setminus\cI$, then $\cP_\lambda=\{\lambda\}$.
  \end{lemma}
  \begin{proof}
    Any such $\lambda$ is the $\bfg$-vector of a cluster monomial, say $x_{k+1}^{\alpha_{k+1}}x_{k+2}^{\alpha_{k+2}}$.
    In this case, the intersection
    \[\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda) \cap \phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)\]
    is precisely $\{\lambda\}$. 
    Indeed, for $k$ odd, the cone $\cC_{k-1}(\phi_{k-1}\lambda)$ lies entirely within a domain of linearity for $\phi_{k-1}^{-1}$.
    In particular, $\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda)$ is a cone containing $\lambda$ directed away from the origin (with walls parallel to the boundary of the domain of linearity containing $\lambda$).
    Next, again for $k$ odd, the cone $\cC_{k+1}(\phi_{k+1}\lambda)$ intersects the domain of linearity for $\phi_{k+1}^{-1}$ containing $\phi_{k+1}\lambda$ in a (possibly degenerate) convex quadrilateral with corners at the origin and $\phi_{k+1}\lambda$.
    In particular, the intersection of $\phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)$ with the cone containing $\lambda$ is a (possibly degenerate) convex quadrilateral with corners at the origin and $\lambda$.
    Combining these observations proves the result for $k$ odd, the case of even $k$ is similar.
  \end{proof}
  To compare with Theorem~\ref{th:dominance inequalities}, we consider three cases in which $\lambda\in\ZZ^2\setminus\cI$:
  \begin{itemize}
    \item if $\lambda_0 \le 0$ and $\lambda_1 \ge 0$, the second and fourth pairs of inequalities become equations for lines which intersect at $\lambda$;
    \item if $\lambda_0 > 0$ and $\lambda_1 \ge \frac{-bc+\sqrt{bc(bc-4)}}{2b}\lambda_0$, the first and second pairs of inequalities become equations for lines which intersect at $\lambda$;
    \item if $\lambda_1 < 0$ and $\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2c}\lambda_1$, the third and fourth pairs of inequalities become equations for lines which intersect at $\lambda$.
  \end{itemize}
  This proves Theorem~\ref{th:dominance inequalities} when $\lambda\notin\cI$.

  Next we aim to understand how inequalities transform under the action of a linear map, this will be the key tool for describing the dominance regions $\cP_\lambda$ for $\lambda\in\cI$.

  \begin{lemma}
    \label{le:transformed inequalities}
    Let $A$ be an invertible $2\times 2$ matrix.
    Under the left action of $A$, say $A\mu=\mu'$ for $\mu,\mu'\in\RR^2$, the region inside $\RR^2$ defined by the inequality $\bfr\bullet\mu \le t$ with $\bfr\in\RR^2$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet\mu'\le t.\]
  \end{lemma}
  \begin{proof}
    This is immediate from the equalities
    \[\bfr\bullet\mu=\bfr^T\mu=\bfr^TA^{-1}A\mu=(A^{-T}\bfr)^TA\mu=(A^{-T}\bfr)\bullet\mu'.\]
  \end{proof}

  \begin{lemma}
    \label{le:dominance inequalities}
    For $k\in\ZZ$, $k\ne0$, and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is determined by the following inequalities when $k>0$:
    \begin{align}
      \label{ineq:1} u_k^-\mu_0+u_{k-1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
      \label{ineq:2} u_{k+1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
      \label{ineq:3} -u_{k-1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
      \label{ineq:4} -u_{k-1}^-\mu_0-u_{k-2}^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;
    \end{align}
    and by the following inequalities when $k<0$:
    \begin{align*}
      u_{k+1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
      u_k^-\mu_0+u_{k-1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
      u_k^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
      -u_{k+2}^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1.
    \end{align*}

@@

    \begin{scope}[shift={(15,0)}]

@@

    \draw (15,-7) node{$\phi_{3}^{-1}\cC_{3}(\phi_{3}\lambda)$};

@@

    For $k=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_k(\phi_k\lambda)\subset\RR^2$ is given by the inequalities 
    \[ (\dagger)\ \mu_0 \le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger)\ -\mu_1\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1. \]
    We inductively compute the region $\phi_{2j}^{-1}\cC_{2j}(\phi_{2j}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{2j}^{-1}=\phi_2^{-j}$.
    First observe that $\phi_2^{-1}=\phi_{-2}$ is given as follows:
    \begin{equation}
      \label{eq:backward two step mutation}
      \phi_{-2}(\lambda)
      =
      \begin{cases}
        \big(-\lambda_0-b\lambda_1, c\lambda_0+(bc-1)\lambda_1\big) & \text{if $\lambda_1\le 0$ and $\lambda_0+b\lambda_1\le 0$;}\\
        (-\lambda_0-b\lambda_1, -\lambda_1) & \text{if $\lambda_1\le 0$ and $\lambda_0+b\lambda_1>0$;}\\
        (-\lambda_0, c\lambda_0-\lambda_1) & \text{if $\lambda_1>0$ and $\lambda_0\le 0$;}\\
        (-\lambda_0,-\lambda_1) & \text{if $\lambda_1>0$ and $\lambda_0>0$.}
      \end{cases}
    \end{equation}

@@

    We see from \eqref{eq:backward two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\ddagger$) lies entirely in the region in which $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$ of determinant 1.
    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $c\mu_0+\mu_1\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1$ which corresponds to (a) with $i=1$.
    Similarly, the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\dagger$) intersects the three domains of linearity in which $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$, each of determinant 1.
    By Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger$) can be seen to transform by these into each of inequalities (b), (c), (d) with $i=1$.
    This establishes the base of an induction on $i$.

    Assuming the inequalities (a)-(d) hold for $i$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_2^{-1}$.
    Both of the boundary rays corresponding to the inequalities (a) and (d) lie entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
    Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
    \[u_{2i+2}^-\mu_0+u_{2i+1}^+\mu_1=(u_3^+u_{2i}^--u_2^-u_{2i-1}^+)\mu_0+(u_2^+u_{2i}^--u_1^-u_{2i-1}^+)\mu_1\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1,\]
    which is the inequality (a) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
    \[-u_{2i+1}^-\mu_0-u_{2i}^+\mu_1=(-u_3^+u_{2i-1}^-+u_2^-u_{2i-2}^+)\mu_0+(-u_2^+u_{2i-1}^-+u_1^-u_{2i-2}^+)\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
    which is the inequality (d) for $i+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
    \[u_{2i+3}^-\mu_0+u_{2i+2}^+\mu_1=(u_3^+u_{2i+1}^--u_2^-u_{2i}^+)\mu_0+(u_2^+u_{2i+1}^--u_1^-u_{2i}^+)\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
    which is the inequality (b) for $i+1$.
    Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
    Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
    \[-u_{2i+1}^-\mu_0-u_{2i}^+\mu_1=(u_1^+u_{2i-1}^--u_2^-u_{2i}^+)\mu_0+(-u_0^+u_{2i-1}^--u_1^-u_{2i}^+)\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
    which is the inequality (d) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
    Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
    Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
    \[-u_{2i+1}^-\mu_0+u_{2i+2}^+\mu_1=(-u_1^+u_{2i+1}^-+u_0^-u_{2i}^+)\mu_0+(u_2^+u_{2i+1}^--u_1^-u_{2i,+})\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
    which is the inequality (c) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
    \[-u_{2i+1}^-\mu_0-u_{2i}^+\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
    which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
    This completes the induction on $i$, proving the Claim and the result for $k$ even.

    For $k=2j+1$, $j\ge0$, and $\lambda\in\cI$, we get $\cC_{2j+1}(\phi_{2j+1}\lambda)\subset\RR^2$ is given by the inequalities 
    \[ (\dagger')\ -\mu_0\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger')\ \mu_1\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1.\]
    Using that $\phi_{2j+1}^{-1}=\phi_2^{-j}\phi_1^{-1}$, we compute the image inductively as above.
    From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{2j+1}(\phi_{2j+1}\lambda)$ corresponding to ($\dagger'$) lies entirely in the region in which $\phi_1^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & 1 \end{array}\right]$ of determinant $-1$.
    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_1^{-1}$ into the inequality $\mu_0\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1$.
    The boundary ray corresponding to ($\ddagger'$) intersects both domains of linearity for $\phi_1^{-1}$ and thus produces the inequalities
    \[ c\mu_0+\mu_1\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1 \qquad\text{and}\qquad \mu_1\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1.\]

@@

  Finally, the inequalities \eqref{ieq3} become more restrictive for $\mu_1\le0$ as $k$ gets larger since the sequence $\frac{-u_k^-}{u_{k-1}^+}$ of negative slopes is monotonically increasing (cf. Lemma~\ref{le:limits}) and the intersection with \eqref{ieq2} (for $k+1$) moves to the right on the $\mu_0$-axis as $k$ increases.
  Thus, following Lemma~\ref{le:limits}, in the limit as $k\to\infty$, we obtain the inequality
  \[ -(\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \le \frac{bc+\sqrt{bc(bc-4)}}{2c}c\lambda_0+b\lambda_1 \]
  determining a boundary of $\cP_\lambda$.

>>>>

  Here we explicitly compute the dominance regions $\cP_\lambda$.
  When $\lambda$ is not imaginary, the dominance region is particularly simple.
  \begin{lemma}
    \label{le:cluster monomials}
    If $\lambda\in\ZZ^2\setminus\cI$, then $\cP_\lambda=\{\lambda\}$.
  \end{lemma}
  \begin{proof}
    Any such $\lambda$ is the $\bfg$-vector of a cluster monomial, say $x_k^{\alpha_k}x_{k+1}^{\alpha_{k+1}}$.
    In this case, the intersection
    \[\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda) \cap \phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)\]
    is precisely $\{\lambda\}$. 
    Indeed, for $k$ odd, the cone $\cC_{k-1}(\phi_{k-1}\lambda)$ lies entirely within a domain of linearity for $\phi_{k-1}^{-1}$.
    In particular, $\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda)$ is a cone containing $\lambda$ directed away from the origin (with walls parallel to the boundary of the domain of linearity containing $\lambda$).
    Next, again for $k$ odd, the cone $\cC_{k+1}(\phi_{k+1}\lambda)$ intersects the domain of linearity for $\phi_{k+1}^{-1}$ containing $\phi_{k+1}\lambda$ in a (possibly degenerate) convex quadrilateral with corners at the origin and $\phi_{k+1}\lambda$.
    In particular, the intersection of $\phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)$ with the cone containing $\lambda$ is a (possibly degenerate) convex quadrilateral with corners at the origin and $\lambda$.
    Combining these observations proves the result for $k$ odd, the case of even $k$ is similar.
  \end{proof}
  To compare with Theorem~\ref{th:dominance inequalities}, we consider three cases in which $\lambda\in\ZZ^2\setminus\cI$:
  \begin{itemize}
    \item if $\lambda_0 \le 0$ and $\lambda_1 \ge 0$, the second and fourth pairs of inequalities become equations for lines which intersect at $\lambda$;
    \item if $\lambda_0 > 0$ and $\lambda_1 \ge \frac{-bc+\sqrt{bc(bc-4)}}{2b}\lambda_0$, the first and second pairs of inequalities become equations for lines which intersect at $\lambda$;
    \item if $\lambda_1 < 0$ and $\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2c}\lambda_1$, the third and fourth pairs of inequalities become equations for lines which intersect at $\lambda$.
  \end{itemize}
  Since $\lambda$ satisfies all the inequalities, these observations prove Theorem~\ref{th:dominance inequalities} when $\lambda\notin\cI$.

  Next we aim to understand how inequalities transform under the action of a piecewise-linear map.
  The following well known fact about linear maps will suffice.

  \begin{lemma}
    \label{le:transformed inequalities}
    Let $A$ be an invertible $2\times 2$ matrix.
    Under the left action of $A$, say $A\mu=\mu'$ for $\mu,\mu'\in\RR^2$, the region inside $\RR^2$ defined by the inequality $\langle\bfr,\mu\rangle \le t$ with $\bfr\in\RR^2$ and $t\in\RR$ is transformed into the region defined by the inequality 
    \[
      \langle A^{-T}\bfr,\mu'\rangle\le t.
    \]
  \end{lemma}
  \begin{proof}
    This is immediate from the equalities
    \[
      \langle \bfr,\mu\rangle
      =
      \bfr^T\mu
      =
      \bfr^TA^{-1}A\mu
      =
      (A^{-T}\bfr)^TA\mu
      =
      \langle A^{-T}\bfr,\mu'\rangle.
    \]
  \end{proof}

  The following calculation is key to our main result.
  \begin{lemma}
    \label{le:dominance inequalities}
    For $k\in\ZZ$, $k\ne0$, and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is determined by the following inequalities when $k>0$:
    \begin{align}
      \label{ineq:1} u_k^-\mu_0+u_{k-1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
      \label{ineq:2} u_{k+1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
      \label{ineq:3} -u_{k-1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
      \label{ineq:4} -u_{k-1}^-\mu_0-u_{k-2}^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;
    \end{align}
    and by the following inequalities when $k<0$:
    \begin{align*}
      u_{k+1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
      u_k^-\mu_0+u_{k-1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
      u_k^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
      -u_{k+2}^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1.
    \end{align*}

@@

    \begin{scope}[shift={(20,0)}]

@@

    \draw (20,-7) node{$\phi_{3}^{-1}\cC_{3}(\phi_{3}\lambda)$};

@@

    For $k=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_k(\phi_k\lambda)\subset\RR^2$ is given by the inequalities 
    \[ (\dagger)\ \mu_0 \le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger)\ -\mu_1\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1. \]
    We compute the region $\phi_{2j}^{-1}\cC_{2j}(\phi_{2j}\lambda)$ using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{2j}^{-1}=\left(\phi_2^{-1}\right)^{j}$.
    First observe that~$\phi_2^{-1}=\phi_{-2}$ is given as follows:
    \begin{equation}
      \label{eq:backward two step mutation}
      \phi_{-2}(\lambda)
      =
      \begin{cases}
        \big(-\lambda_0-b\lambda_1, c\lambda_0+(bc-1)\lambda_1\big) & \text{if $\lambda_1\le 0$ and $\lambda_0+b\lambda_1\le 0$;}\\
        (-\lambda_0-b\lambda_1, -\lambda_1) & \text{if $\lambda_1\le 0$ and $\lambda_0+b\lambda_1>0$;}\\
        (-\lambda_0, c\lambda_0-\lambda_1) & \text{if $\lambda_1>0$ and $\lambda_0\le 0$;}\\
        (-\lambda_0,-\lambda_1) & \text{if $\lambda_1>0$ and $\lambda_0>0$.}
      \end{cases}
    \end{equation}

@@

    We prove the claim by induction on $i$.
    We see from \eqref{eq:backward two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\ddagger$) lies entirely in the region in which $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$.
    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $c\mu_0+\mu_1\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1$ which corresponds to (a) with $i=1$.
    Similarly, the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\dagger$) intersects the three domains of linearity in which $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$.
    By Lemma~\ref{le:transformed inequalities}, the inequality~($\dagger$) can be seen to transform by these into each of inequalities (b), (c), (d) with~$i=1$.
    This establishes the base of our induction.

    Assuming the inequalities (a)-(d) hold for $i$, we apply Lemma~\ref{le:transformed inequalities} for $\phi_2^{-1}$.
    Both of the boundary rays corresponding to the inequalities (a) and (d) lie entirely in the region where $\phi_2^{-1}$ acts according to the matrix~$\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
    Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
    \[u_{2i+2}^-\mu_0+u_{2i+1}^+\mu_1=(u_3^+u_{2i}^--u_2^-u_{2i-1}^+)\mu_0+(u_2^+u_{2i}^--u_1^-u_{2i-1}^+)\mu_1\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1,\]
    which is the inequality (a) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
    \[-u_{2i+1}^-\mu_0-u_{2i}^+\mu_1=(-u_3^+u_{2i-1}^-+u_2^-u_{2i-2}^+)\mu_0+(-u_2^+u_{2i-1}^-+u_1^-u_{2i-2}^+)\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
    which is the inequality (d) for $i+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
    \[u_{2i+3}^-\mu_0+u_{2i+2}^+\mu_1=(u_3^+u_{2i+1}^--u_2^-u_{2i}^+)\mu_0+(u_2^+u_{2i+1}^--u_1^-u_{2i}^+)\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
    which is the inequality (b) for $i+1$.
    Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
    Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
    \[-u_{2i+1}^-\mu_0-u_{2i}^+\mu_1=(u_1^+u_{2i-1}^--u_2^-u_{2i}^+)\mu_0+(-u_0^+u_{2i-1}^--u_1^-u_{2i}^+)\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
    which is the inequality (d) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
    Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
    Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
    \[-u_{2i+1}^-\mu_0+u_{2i+2}^+\mu_1=(-u_1^+u_{2i+1}^-+u_0^-u_{2i}^+)\mu_0+(u_2^+u_{2i+1}^--u_1^-u_{2i,+})\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
    which is the inequality (c) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
    \[-u_{2i+1}^-\mu_0-u_{2i}^+\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
    which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
    This completes the induction on $i$, proving the Claim and the result for $k$ even.

    For $k=2j+1$, $j\ge0$, and $\lambda\in\cI$, we get $\cC_{2j+1}(\phi_{2j+1}\lambda)\subset\RR^2$ is given by the inequalities 
    \[ (\dagger')\ -\mu_0\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger')\ \mu_1\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1.\]
    Using that $\phi_{2j+1}^{-1}=\left(\phi_2^{-1}\right)^j\phi_1^{-1}$, we compute the image inductively as above.
    From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{2j+1}(\phi_{2j+1}\lambda)$ corresponding to ($\dagger'$) lies entirely in the region in which $\phi_1^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & 1 \end{array}\right]$.
    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_1^{-1}$ into the inequality $\mu_0\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1$.
    The boundary ray corresponding to ($\ddagger'$) intersects both domains of linearity for $\phi_1^{-1}$ and thus produces the inequalities
    \[ c\mu_0+\mu_1\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1 \qquad\text{and}\qquad \mu_1\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1.\]

@@

  Finally, the inequalities \eqref{ieq3} become more restrictive for $\mu_1\le0$ as $k$ gets larger since the sequence $\frac{-u_k^-}{u_{k-1}^+}$ of negative slopes is monotonically increasing (cf. Lemma~\ref{le:limits}) and the intersection with \eqref{ieq2} (for $k+1$) moves to the right on the $\mu_0$-axis as $k$ increases.
  Thus, following Lemma~\ref{le:limits}, in the limit as $k\to\infty$, we obtain the inequality below determining a boundary of $\cP_\lambda$:
  \[ -(\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \le \frac{bc+\sqrt{bc(bc-4)}}{2c}c\lambda_0+b\lambda_1. \]
